
\sectionwp{Preface}
Before I started this thesis, my knowledge about space technology was close to zero. Nevertheless, when I was told about the possibility of working in the project of building the first satellite that Finland will launch into space, I did not hesitate for a second. Working in the project was great opportunity and I had to take it.

My work has been done at the Department of Radio Science and Engineering of Aalto University and my main goal has been to produce good software for the ground segment of the mission. It has been really challenging, but it has also given me the chance to gain knowledge in several space related areas which some months ago where somehow like magic for me.

It has been real pleasure being a small part of this project. I believe these satellites are the present and future for universities, and they can help students see that all the effort they put during their studies can accomplish something as amazing as putting their own satellite into orbit.


\thispagestyle{plain}
\pagebreak

\sectionwp{Acknowledgements}

I cannot start in any other way than thanking my parents, Manuel and María del Carmen. Without you this would not be happening, thank you for your constant love and trust. Thank you for everything you have taught me and keep teaching me everyday. Also, thank you for your great support when I decided to move abroad. I love you.\\

Thanks to Aalto University, especially to Jaan Praks, who invited me to participate in the great adventure that is Aalto-1 and has supervised my thesis. Also, many thanks to the Aalto-1 team. It has been great working with you.\\

Many thanks to Urmas Kvell and the ESTCube team. Thank you for your cooperation during my visits to Estonia and also for your invitation to stay at the Tõravere Observatory for two weeks. My stay there was very fruitful  and interesting.\\

I would also like to thank Gonzalo Mariscal, International Manager of the School of Engineering at Universidad Europea de Madrid. Thank you for your support during these two years and also for all the times I bothered you with questions before I moved to Finland.\\

Finally, I want to say thanks to all the friends who have helped me since I came to the country; especially to Adrián Yanes, who convinced me to come to Finland in the first place and has been a great friend for the last eight years. Also Borja Tarrasó, whose support and friendship since I arrived have been very important to me. You guys have always been there, thanks. In addition, I do not want to forget Alberto Alonso, one of the last additions to our group whom has proved to be a great friend. Last, but not least, I want to thank Tuomo Ryynänen and his family. You have made me feel very welcomed in your country. I hope that, in the future, I will be able to reciprocate in mine.\\




\vspace{1cm}
Otaniemi, Espoo, August 2013.

\vspace{0.5cm}
David.
\thispagestyle{plain}
\pagebreak

\tableofcontents

\pagebreak
